\Huge ACM and Climate Change

### 2019-05-25 main.tex
An outline for the carbon offset part

\bcp{Polish and expand with reworked old text and new points.}
Finally, we can start imposing a cost on ourselves by using carbon
offsets.  (People counter-argue that this "lets people off the hook" and
encourages inaction, but we believe it is consistent with encouraging action
-- again, if offsets are priced right.)

>>>>

Finally, we can start imposing a cost on ourselves by using carbon
offsets.  
\begin{itemize}
\item There are two good reasons for doing this, as well as some significant
concerns.
\begin{itemize}
\item Reasons in favor:
\begin{itemize}
\item It is the right thing to do: We should be changing our behavior
starting now, and giving ourselves a ``price signal''
\item Offsets reduce carbon emissions now.  (Yes, there are bogus ones, but
not all are bogus.)
\end{itemize}
\item Concerns:
\end{itemize}
\item It is hard to choose the price (right now there is an oversupply), and setting it too low leads to complacency
\item Organizations are not set up to do it.  Our experience with getting
ACM to introduce an offsetting policy shows that it requires significant
effort.
\end{itemize}
People counter-argue that this "lets people off the hook" and
encourages inaction, but we believe it is consistent with encouraging action
-- again, if offsets are priced right.
